---
title: "simpleRegress"
author: "Alma Andreasian"
date: "Fall 2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Introduction

We are  trying to find a  a variable that is a better  predictor of the LENGTH of a bear than is a NECK size.


## make a simple regression model

```{r}
bears <- read.csv(file="BEARS.csv",header = TRUE)
```

## Model LENGTH ~ NECK  this is an example  

```{r}
simp <- lm(LENGTH~NECK,data=bears)
plot(LENGTH~NECK,data=bears)
abline(simp)
summary.lm(simp)
```

NECK as a variable for determining a bears LENGTH and adjusted R square score of 0.7476

The scatter plot shows that as NECK size goes up, LENG%H does as well , thus
NECK size is a good predictor to determine LENGTH.

## now predict the length of a bear who has a neck of 17, 22 and 26


```{r}
new <- data.frame(NECK=c(17,22,26))
predict(simp,new)
predict(simp,new,se.fit=TRUE, interval="prediction")
```

## Numerical Summary

```{r}
cor(bears$LENGTH,bears$NECK)
```


## Surely there is another variable that can better predict LENGTH than NECK. Find one and compare its performance to that of neck by it value of Adjusted-Rsquared (bigger is better).


```{r}
simp <- lm(LENGTH~CHEST,data=bears)
plot(LENGTH~CHEST,data=bears)
abline(simp)
summary.lm(simp)
```

CHEST is a variable for determining a bears LENGTH had an adjustex R squared score of 0.7869.

The scatter plot shows that as CHEST size goes up, LENGTH does as well. Thus CHEST size is a good predictor to determine the LENGTH of the bear.

## Numerical Summary


```{r}
cor(bears$LENGTH,bears$CHEST)
```

The correlation is coefficient

## Conclusion

CHEST had adjusted R Squared score of 0.7869 While NECK had an adjsted R squared of 0.7476.

CHEST is a better predictor of LENGTH than NECK is, because the adjusted R squared of the fit for CHEST was larger than the adjusted R squared of the fit for NECK. 